### 2014-07-23 fundamentals/impl.tex
more topic sentences

\subsection{Dynamically loadable libraries}
% (diagram)
\subsection{Agent Interchangability}
% interchangeability due to exchange behavior api
\subsection{Region/Institution/Facility hierarchy}
% (diagram)
\subsection{Discrete Object Tracking}
% Resources, Materials (note isotope tracking, decay behavior)
\subsection{Toolkit}
% library of tools
% contributions to the toolkit
% place for metrics
\subsection{Cycamore}
% base modules

>>>>

\subsection{Cluster-Ready Software}

Because this doesn't rely on PowerSim, GoldSim, Excel, or any other COTS 
Windows-based software, we can run singular instances of Cyclus 
on large linux machines that have lots more capability than hacked together 
Windows clusters.

\subsection{Dynamically loadable libraries}
% (diagram)

A key innovation that has previously not been implemented in nuclear fuel cycle 
simulators in the literature is implementing this generic API and modular 
architecture into a suite of dynamically loadable ``plug-in'' libraries.

This approach allows contribution to an ecosystem of libraries. The 
scientist-developer can therefore focus on generating a model within their 
sphere of expertise, while relying on the model contributions of others to fill 
in the other technologies.

This is implemented largely through a clean API and a modern build system.

\subsection{Agent Interchangability}
% interchangeability due to exchange behavior api

This approach enables ``apples-to-apples'' comparisons, something that has been 
sorely missing in previous simulators.

By making the facilities interchangeable, it combinatorically increases the 
number of scenarios that can be modeled. The user can choose to model just the 
front end or just the back end of a fuel cycle.

This is implemented with an API that focuses on treating the agents as black 
boxes.

\subsection{Region/Institution/Facility hierarchy}
% (diagram)

Not many fuel cycle simulators have this, it turns out. We used to implement 
this with inheritance. Now I'm not so sure. . . <insert recent knowledge here>.

\subsection{Discrete Object Tracking}
% Resources, Materials (note isotope tracking, decay behavior)

Discrete facility and material tracking is more realistic an dmore

\subsection{Toolkit}
% library of tools
% contributions to the toolkit
% place for metrics

The toolkit is a place for developers and users to contribute common-use tools 
for calculating metrics, managing process physics, handling data.

This was implemented by liberal use of namespaces  and is populated with an 
introductory suite of useful tools.

\subsection{Cycamore}
% base modules

Cycamore contains a number of usefule facility models that are a mere base-set. 
Additional modules are needed for full fuel cycle simulation. However, simple 
fuel cycles can be generated with Cycamore and Cyclus alone.

<diagram of a possible Cycamore-only simulation>
